Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-06-18 lqg-strings.tex
Moved "two expressions for area" section to appendix
relocated some stuff and rewrote what needed to be rewritten

\subsection{Modified Equations of Motion}\label{sec:modified-eom}

@@

In the same way we considered the quantum geometry inverse metric correction to the Nambu-Goto action, it is also natural to consider such correction to the Polyakov action. We start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
\begin{multline} \label{eqn:inverse-metric-Polyakov}
	S_{I A P} = - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times \\ \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
\end{multline}
One might think this action is incomplete since we only applied the correction to the determinant and didn't change the inverse metric $g^{a b}$, however the correction \ref{eqn:inverse-metric-correction} is a correction to the \emph{area} of the WS, not its metric. Moreover, there are other good reasons for this form of the Polyakov action: the first is that the action in this form, as we shall see, reduces neatly to the area-corrected Nambu-Goto action \eqref{eqn:modified-NG-action}, and the second comes from a more rigorous bimetric Polyakov string analysis which will be done in appendix \ref{app:bimetric-string}, where we show that starting from a bimetric Polyakov string one can derive the action \eqref{eqn:inverse-metric-Polyakov}.

This action is even more manifestly background Poincaré invariant, since now the $X^{\mu}$ dependence is explicit with this being a first-order action with $g_{a b}$ and $X^{\mu}$ treated as independent variables. This time, however, we lose WS Weyl symmetry, since the second term has inverse determinant multiplied by inverse metric.

The equations of motion for the world-sheet metric are completely unchanged by this correction,
\begin{equation} \label{eqn:vary-wrt-g}
	\frac{\delta S_{I A P}}{\delta g^{c d}} = 0
\end{equation}
which leads to the stress-energy tensor for the worldsheet:
\begin{multline} \label{eqn:inverse-area-em-tensor}
	T_{c d} := \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \\ - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0 ,
\end{multline}
from which we can extract the metric $g_{c d}$ as
\begin{equation} \label{eqn:ws-metric}
	g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
\end{equation}
where the function $f$ is given by
\begin{equation} \label{eqn:inverse-area-f}
	\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
\end{equation}

As for variation w.r.t the embbeding fields $X^{\lambda}$, we have
\begin{equation} \label{eqn:vary-wrt-X}
	\frac{\delta S_{I A P}}{\delta X^{\lambda}} = 0
\end{equation}
\begin{multline} \label{eqn:X-eom-inverse-area}
	F^{-} \sqrt{- g} g^{a b} \partial _{a} \partial _{b} X^{\nu} G_{\lambda \nu} + \partial _{a} \left( F^{-} \sqrt{- g} g^{a b} \right) \partial _{b} X^{\nu} G_{\lambda \nu} = \\ = \frac{1}{2} F^{-} \sqrt{- g} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \partial _{\lambda} G_{\mu \nu} ,
\end{multline}
where
\begin{equation} \label{eqn:F-minus-def}
	F^{-} \equiv 1 - \frac{k \Delta}{2 (- g)} .
\end{equation}
Since all 2-dimensional metrics are conformally flat \cite{Schottenloher}, we use conformal gauge $g_{a b} = \e ^{\phi (x)} \eta _{a b}$ and assume flat background $G_{\mu \nu} = \eta _{\mu \nu}$, to simplify eq (\ref{eqn:X-eom-inverse-area}) into
\begin{equation} \label{eqn:X-eom-simplified}
	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \frac{1}{F^{-}} \eta ^{a b} \partial _{a} F^{-} \partial _{b} X^{\mu} = 0 .
\end{equation}
By expanding the definition of $F^{-}$ we get
\begin{equation} \label{eqn:coupling-X-phi}
	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \eta ^{a b} \frac{\left( 2 \del _{a} \phi - \del _{a} \ln (\Delta) \right)}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} \del _{b} X^{\mu} = 0 ,
\end{equation}
revealing a wave equation sourced by a coupling between the WS conformal factor, quantum of area field $\Delta$ and the embedding fields much akin to the dilaton field \cite{Balthazar-t-backgrounds}. We'll come back to this in \autoref{sec:discussion}.

@@

Equation(\ref{eqn:X-eom-simplified}) seems a bit odd, but we can polish it by choosing a plane-wave ansatz for the embedding fields $X^{\mu} = X^{\mu} _{0} \e ^{-i (E \tau - p \sigma)}$ and using it to fix a form for the conformal factor $\e ^{\phi (x)}$ appearing in $F^{-}$. By using the ansatz in eq(\ref{eqn:X-eom-simplified}), it becomes
\begin{equation}
	(E^{2} - p^{2}) X^{\mu} + i (E \partial _{\tau} \ln (F^{-}) - p \partial _{\sigma} \ln (F^{-})) X^{\mu} = 0 ,
\end{equation}
from which we can use the freedom in the conformal factor to fix the second term as $- m^2 X^{\mu}$, with $- m^2 = p^2 - E^2$ on-shell and this, in turn, implies that the derivatives of $\ln (F^{-})$ are given by
\begin{equation} \label{eqn:derivatives-F-minus}
	\partial _{\tau} \ln (F^{-}) = i E , \ \partial _{\sigma} \ln (F^{-}) = i p ,
\end{equation}
thus we have
\begin{equation} \label{eqn:ln-F}
	\ln (F^{-}) = i (E \tau + p \sigma) + a , \ a \in \mathbb{C}
\end{equation}

\begin{equation} \label{eqn:F-minus-exp}
	F^{-} = A \e ^{i (E \tau + p \sigma)} , \ A \in \C
\end{equation}
\begin{equation} \label{eqn:phi}
	\e ^{\phi (x)} = \sqrt{\frac{k \Delta}{2 \left( 1 - A \e ^{i (E \tau + p \sigma)} \right)}} .
\end{equation}
At first glance, it seems problematic that we have a complex conformal factor, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it should also pick the respective component of $\e ^{\phi}$. With this choice, we thus turned eq(\ref{eqn:X-eom-simplified}) into a Klein-Gordon equation
\begin{equation} \label{eqn:X-Klein-Gordon-eqn}
	\left( \partial _{\sigma} ^2 - \partial _{\tau} ^2 \right) X^{\mu} - \mu ^2 X^{\mu} = 0 .
\end{equation}
The imposition that
\begin{equation} \label{eqn:mu-constraint-1}
	i (E \partial _{\tau} \ln (F^{-}) - p \partial _{\sigma} \ln (F^{-})) = - \mu ^2
\end{equation}
can be used to find the explicit dependence of $\mu ^2$ with the quantum geometry parameters $k \Delta$ as in
\begin{multline} \label{eqn:mu-constraint-final}
	\mu ^2 = \frac{i}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} \big( p \del _{\sigma} \ln \left( \e^{2 \phi} / \Delta \right) - \\
	- E \del _{\tau} \ln \left( \e^{2 \phi} / \Delta \right) \big) .
\end{multline}

\subsection{Relation With The Nambu-Goto Analysis} \label{sec:relation-with-NG-case}

At first glance, our recent analysis of the Polyakov string with inverse metric correction seems to not be related to what we found in the analysis of the Nambu-Goto string. However, as pointed out in \cite{Grimshaw2010Homogenization}, wave equations with a variable speed (the result of the Nambu-Goto analysis) can be turned into Klein-Gordon equations (what we just found). While their work deals only with space-varying wave speed, it is straightforward to generalise the procedure to also include time dependence.

Following the procedure found in \cite{Grimshaw2010Homogenization}, we start with eq(\ref{eqn:simplified-modified-wave-eqn}) obtained in sec(\ref{sec:modified-eom}), renaming $\sigma$ as $x$ and dividing by $(F^{+})^2$ such that we have $v^2$ on the second term like the mentioned work, and perform a change of variables $(t , x) \rightarrow (\tau (t , x) , \sigma (t , x))$, where without loss of generality (one needs just to rescale and/or rotate the coordinates) we set
\begin{multline} \label{eqn:new-coordinates-constraints-quadratic}
	\ \ \ \ \ \ \ \ \ \ (\partial _{t} \sigma)^2 - v^2 (\partial _{x} \sigma)^2 = v^2 (\partial _{x} \tau)^2 - (\partial _{t} \tau)^2 \\
	\partial _{t} \tau \partial _{t} \sigma = v^2 \partial _{x} \tau \partial _{x} \sigma , \ \ \ \ \ \ \ \ \ \ \ \
\end{multline}
or more compactly,
\begin{multline} \label{eqn:new-coordinates-constraints-compact}
	\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \partial _{t} \tau = v \partial _{x} \sigma \\
	\partial _{t} \sigma = v \partial _{x} \tau \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ ,
\end{multline}
which is equivalent to
\begin{multline} \label{eqn:new-coordinates-constraints-second-order}
	\ \ \ \ \ \ \ \ \ \ \ \partial _{t} ^2 \tau - v^2 \partial _{x} ^2 \tau = \partial _{t} v \partial _{x} \sigma + v \partial _{x} v \partial _{x} \tau \\
	\partial _{t} ^2 \sigma - v^2 \partial _{x} ^2 \sigma = \partial _{t} v \partial _{x} \tau + v \partial _{x} v \partial _{x} \sigma . \ \ \ \ \ \ \
\end{multline}
This turns eq(\ref{eqn:simplified-modified-wave-eqn}) into
\begin{multline} \label{eqn:modified-wave-eqn-new}
	\partial _{\tau} ^2 X^{\mu} - \partial _{\sigma} ^2 X^{\mu} + \\
	+ \frac{\partial _{t} v \partial _{x} \sigma + v \partial _{x} v \partial _{x} \tau}{((\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2)} \partial _{\tau} X^{\mu} + \\
	+ \frac{\partial _{t} v \partial _{x} \tau + v \partial _{x} v \partial _{x} \sigma}{((\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2)} \partial _{\sigma} X^{\mu} = 0 .
\end{multline}
Next, we introduce $X^{\mu} = \kappa (\tau , \sigma) W^{\mu} (\tau , \sigma)$ such that terms proportional to first derivatives of $W^{\mu}$ cancel out. This is obtained by choosing $\kappa = v^{1/2}$ and concluding that $v$ only depends on $x$. With this, eq(\ref{eqn:modified-wave-eqn-new}) turns into a Klein-Gordon equation
\begin{equation}
	\partial _{\tau} ^2 W^{\mu} - \partial _{\sigma} ^2 W^{\mu} + \mu ^2 W^{\mu} = 0 ,
\end{equation}
with \textquotedblleft mass" squared given by
\begin{equation}
	\mu ^2 = \frac{(\partial _{x} v)^2 - 2 v \partial _{x} ^2 v}{4 \left( (\partial _{t} \tau)^2 - v^2 (\partial _{x} \tau)^2 \right)}
\end{equation}
and $\tau (t , x)$ satisfying constraints(\ref{eqn:new-coordinates-constraints-compact}). This shows that our action(\ref{eqn:inverse-metric-Polyakov}) is indeed in agreement with the inverse area corrected Nambu-Goto action(\ref{eqn:modified-NG-action}).

@@

When looking at the constraints, we see that we can't decouple the exponentials in $\tau$ from any of the sums, thus we get two-index \textquotedblleft Virasoro modes"
\begin{align}
	L_{n , p} := \alpha ^{\mu} _{n} \alpha ^{\nu} _{p} \eta _{\mu \nu}                                                         & = 0 , \ \forall \ n , p \in \mathbb{Z} , \label{eqn:"virasoro"-modes-1} \\
	\widetilde{L}_{n , p} := \alpha ^{\mu} _{n} (\alpha ^{\nu} _{p})^{*} \eta _{\mu \nu}                                       & = 0 , \ n \neq p , \label{eqn:"virasoro"-modes-2}                       \\
	\sum _{n} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) & = 0 \label{eqn:"virasoro"-modes-sum} .
\end{align}
Constraint \eqref{eqn:"virasoro"-modes-2} implies that we only have $D$ independent expansion modes for each field $X^{\mu}$, which for consistency as we will see later means $\alpha ^{\mu} _{- p} = \alpha ^{\mu} _{p} , \ p \leq d = D - 1$ and $\alpha ^{\mu} _{n} = 0 , \ \forall \ |n| > d$, so we have a truncated solution. This is not surprising, since because space-time is discrete we expect wavelengths smaller than the granular structure to be ruled out.

@@

We now seek to quantize the Klein-Gordon string by means of covariant canonical quantization, in a manner much similar to those found in (\cite{Tong2009Lectures},\cite{Green2012Superstring}). The string coordinates $X^{\mu}$ and it's conjugate momentum $\Pi ^{\nu}$ are turned into operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$, with the Poisson brackets $\{ . , . \}$ being replaced by commutators $[ . , . ] = i \hbar \{ . , . \}$:
\begin{align}
	\left[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \right] & = i \delta (\sigma - \sigma ') \eta ^{\mu \nu} \label{eqn:X-P-commutator}                                              \\
	\left[ \Hat{X}^{\mu} , \Hat{X}^{\nu} \right]                                     & = 0 = \left[ \Hat{\Pi}^{\mu} , \Hat{\Pi}^{\nu} \right] \label{eqn:X-X-P-P-commutators}                                 \\
	\left[ \Hat{a}^{\mu} _{n} , \Hat{a}^{\nu} _{p} \right]                           & = 0 = \left[ (\Hat{a}^{\mu} _{n})^{\dagger} , (\Hat{a}^{\nu} _{p})^{\dagger} \right] \label{eqn:a-a-a*-a*-commutators} \\
	\left[ \Hat{a}^{\mu} _{n} , (\Hat{a}^{\nu} _{p})^{\dagger} \right]               & = \delta _{|n| , |p|} \eta ^{\mu \nu} \label{eqn:a-a*-commutator}                                                      \\
	\left[ \Hat{x}^{\mu} , \Hat{x}^{\nu} \right]                                     & = 0 = \left[ \Hat{p}^{\mu} , \Hat{p}^{\nu} \right] \label{eqn:x-x-p-p-commutators}                                     \\
	\left[ \Hat{x}^{\mu} , \Hat{p}^{\nu} \right]                                     & = i \eta ^{\mu \nu} \label{eqn:x-p-commutator}
\end{align}

@@

\subsection{Two Expressions for Area}\label{eqn:area-formulae}

@@

\section{Worldsheet Action in Terms of Transverse Velocity}\label{app:transverse-action}

\subsection{The Bimetric Polyakov Equations} \label{sec:bimetric-polyakov-eoms}

>>>>

\subsection{(Worldsheet) Kalb Ramond and Area Quantization} \label{sec:ws-kalb-ramond}

In the following, we will derive the equations of motion for the bimetric Polyakov action and along the way we will discover that the scalar density $\Delta(x)$ can be identified as being the determinant of (a tensor proportional to) the antisymmetric tensor $\widetilde{\varepsilon}_{a c}$ living on the worldsheet. The worldsheet antisymmetric tensor can itself be understood as arising from the pullback of a bulk antisymmetric tensor. Now, in string theory, there is already a very important antisymmetric bulk tensor called the Kalb-Ramond field.

Following the usual procedure such as the one found in \cite{Tong2009Lectures}, we find two copies of the string energy-momentum tensor:
\begin{equation} \label{eqn:variation-wrt-g}
	\frac{\delta S_{P B}}{\delta g^{c d}} = 0
\end{equation}
\begin{multline} \label{eqn:g-em-tensor}
	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T} \frac{\delta S_{int}}{\delta g^{c d}} ,
\end{multline}
and completely analogous for the $H_{\mu \nu}$ metric,
\begin{equation} \label{eqn:variation-wrt-h}
	\frac{\delta S_{P B}}{\delta h^{c d}} = 0
\end{equation}
\begin{multline} \label{eqn:h-em-tensor}
	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T'} \frac{\delta S_{int}}{\delta h^{c d}} .
\end{multline}
If we assume no interaction term $S_{int} = 0$, we get the expected expressions for the auxiliary metrics $g_{c d}$ and $h_{c d}$ as in
\begin{equation} \label{eqn:g-expression}
	g_{c d} = 2 f^{(G)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
\end{equation}
where the function $f^{(G)}$ is given by
\begin{equation} \label{eqn:g's-f-function}
	\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}
\end{equation}
and for $h_{c d}$
\begin{equation} \label{eqn:h-expression}
	h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} ,
\end{equation}
with $f^{(H)}$ given by
\begin{equation} \label{eqn:h's-f-function}
	\frac{1}{f^{(H)}} = h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} .
\end{equation}
If the auxiliary metrics $g_{c d}$ and $h_{c d}$ coincide with the pullback metrics from $G_{\mu \nu}$ and $H_{\mu \nu}$, the action with no interaction reduces to
\begin{equation} \label{eqn:double-NG-action}
	S = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h} ,
\end{equation}
and from here we note that if $T' = - T k / 2$ and $h = \Delta ^2 / g$, we recover the Nambu-Goto area-corrected action \eqref{eqn:modified-NG-action}
\begin{equation} \label{eqn:area-corrected-NG-from-bimetric}
	S = - T \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) .
\end{equation}
The condition $h = \Delta ^2 / g$ can be achieved by
\begin{equation} \label{eqn:h=SgS}
	h_{a b} = \Delta _{a c} \Delta _{b d} g^{c d} .
\end{equation}
This implies that
\begin{multline} \label{eqn:SgS-implication}
	\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \widetilde{\varepsilon} ^{c c'} \Delta _{b d} \widetilde{\varepsilon} ^{d d'} G_{\mu \nu} \right) \times \\
	\times \del _{c'} X^{\mu} \del _{d'} X^{\nu} = 0 ,
\end{multline}
which can be achieved if
\begin{equation} \label{eqn:S=sigma_y}
	\Delta _{a c} = \sqrt{\Delta} \widetilde{\varepsilon} _{a c}
\end{equation}
and if the background metrics are related by
\begin{equation} \label{eqn:H=1/(2g)G}
	H_{\mu \nu} = \frac{\Delta}{2 g} G_{\mu \nu} .
\end{equation}
This makes sense since $\Delta _{a b}$ is related to area, so it should be a 2-form. Now, since the WS metric $g_{a b}$ is taken as the pullback of the bulk metric $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$, which is part of the closed string spin-2 spectrum, then it would make sense for the WS area 2-form $\Delta _{a b}$ to be (at least related to) the pullback of the Kalb-Ramond field, which is the other half of the closed string rank 2 tensor field excitations,
\begin{equation} \label{eqn:Delta-B-relation}
	\Delta _{a b} \sim \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} .
\end{equation}

If we impose the conditions \eqref{eqn:h=SgS}, \eqref{eqn:S=sigma_y} and \eqref{eqn:H=1/(2g)G} plus $T' = - T k / 2$ in the interactionless bimetric Polyakov action \eqref{eqn:polyakov-flat}, we obtain the Polyakov version of the area-corrected action \eqref{eqn:modified-NG-action}:
\begin{multline} \label{eqn:inverse-metric-Polyakov}
	S_{I A P} = - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times \\ \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
\end{multline}

@@

In this section, we explore the action \eqref{eqn:inverse-metric-Polyakov} derived previously. This action is even more manifestly background Poincaré invariant, since now the $X^{\mu}$ dependence is explicit with this being a first-order action with $g_{a b}$ and $X^{\mu}$ treated as independent variables. However, the price to pay is that we don't have WS Weyl symmetry since the second term has inverse determinant multiplied by inverse metric.

The equations of motion for the world-sheet metric are completely unchanged by this correction,
\begin{equation} \label{eqn:vary-wrt-g}
	\frac{\delta S_{I A P}}{\delta g^{c d}} = 0
\end{equation}
which leads to the stress-energy tensor for the worldsheet:
\begin{multline} \label{eqn:inverse-area-em-tensor}
	T_{c d} := \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \\ - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0 ,
\end{multline}
from which we can extract the metric $g_{c d}$ as
\begin{equation} \label{eqn:ws-metric}
	g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
\end{equation}
where the function $f$ is given by
\begin{equation} \label{eqn:inverse-area-f}
	\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}
\end{equation}
just like the regular ST literature.

As for variation \wrt the embbeding fields $X^{\lambda}$, we have
\begin{equation} \label{eqn:vary-wrt-X}
	\frac{\delta S_{I A P}}{\delta X^{\lambda}} = 0
\end{equation}
\begin{multline} \label{eqn:X-eom-inverse-area}
	F^{-} \sqrt{- g} g^{a b} \partial _{a} \partial _{b} X^{\nu} G_{\lambda \nu} + \partial _{a} \left( F^{-} \sqrt{- g} g^{a b} \right) \partial _{b} X^{\nu} G_{\lambda \nu} = \\ = \frac{1}{2} F^{-} \sqrt{- g} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \partial _{\lambda} G_{\mu \nu} ,
\end{multline}
where
\begin{equation} \label{eqn:F-minus-def}
	F^{-} \equiv 1 - \frac{k \Delta}{2 (- g)} .
\end{equation}
Since all 2-dimensional metrics are conformally flat \cite{Schottenloher}, we use conformal gauge $g_{a b} = \e ^{\phi (x)} \eta _{a b}$ and assume flat background $G_{\mu \nu} = \eta _{\mu \nu}$, to simplify eq (\ref{eqn:X-eom-inverse-area}) into
\begin{equation} \label{eqn:X-eom-simplified}
	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \frac{1}{F^{-}} \eta ^{a b} \partial _{a} F^{-} \partial _{b} X^{\mu} = 0 .
\end{equation}
By expanding the definition of $F^{-}$ we get
\begin{equation} \label{eqn:coupling-X-phi}
	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \eta ^{a b} \frac{\left( 2 \del _{a} \phi - \del _{a} \ln (\Delta) \right)}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} \del _{b} X^{\mu} = 0 ,
\end{equation}
revealing a wave equation sourced by a coupling between the WS conformal factor, quantum of area field $\Delta$ and the embedding fields much akin to the dilaton field \cite{Balthazar-t-backgrounds}. We'll come back to this in \autoref{sec:discussion}.

@@

Equation (\ref{eqn:X-eom-simplified}) seems a bit odd, but we can polish it by choosing a plane-wave ansatz for the embedding fields $X^{\mu} = X^{\mu} _{0} \e ^{-i (E \tau - p \sigma)}$ and using it to fix a form for the conformal factor $\e ^{\phi (x)}$ appearing in $F^{-}$. By using the ansatz in eq (\ref{eqn:X-eom-simplified}), it becomes
\begin{equation}
	(E^{2} - p^{2}) X^{\mu} + i (E \partial _{\tau} \ln (F^{-}) - p \partial _{\sigma} \ln (F^{-})) X^{\mu} = 0 ,
\end{equation}
from which we can use the freedom in the conformal factor to fix the second term as $- m^2 X^{\mu}$, with $- m^2 = p^2 - E^2$ on-shell and this, in turn, implies that the derivatives of $\ln (F^{-})$ are given by
\begin{equation} \label{eqn:derivatives-F-minus}
	\partial _{\tau} \ln (F^{-}) = i E , \ \partial _{\sigma} \ln (F^{-}) = i p ,
\end{equation}
thus we have
\begin{equation} \label{eqn:ln-F}
	\ln (F^{-}) = i (E \tau + p \sigma) + a , \ a \in \mathbb{C}
\end{equation}

\begin{equation} \label{eqn:F-minus-exp}
	F^{-} = A \e ^{i (E \tau + p \sigma)} , \ A \in \C
\end{equation}
\begin{equation} \label{eqn:phi}
	\e ^{\phi (x)} = \sqrt{\frac{k \Delta}{2 \left( 1 - A \e ^{i (E \tau + p \sigma)} \right)}} .
\end{equation}
At first glance, it seems problematic that we have a complex conformal factor, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it should also pick the respective component of $\e ^{\phi}$. With this choice, we thus turned eq (\ref{eqn:X-eom-simplified}) into a Klein-Gordon equation
\begin{equation} \label{eqn:X-Klein-Gordon-eqn}
	\left( \partial _{\sigma} ^2 - \partial _{\tau} ^2 \right) X^{\mu} - \mu ^2 X^{\mu} = 0 .
\end{equation}
The imposition that
\begin{equation} \label{eqn:mu-constraint-1}
	i (E \partial _{\tau} \ln (F^{-}) - p \partial _{\sigma} \ln (F^{-})) = - \mu ^2
\end{equation}
can be used to find the explicit dependence of $\mu ^2$ on the quantum geometry parameters $k \Delta$ as in
\begin{multline} \label{eqn:mu-constraint-final}
	\mu ^2 = \frac{i}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} \big( p \del _{\sigma} \ln \left( \e^{2 \phi} / \Delta \right) - \\
	- E \del _{\tau} \ln \left( \e^{2 \phi} / \Delta \right) \big) .
\end{multline}

@@

When looking at the constraints, we see that we can't decouple the exponentials in $\tau$ from any of the sums, thus we get two-indices \textquotedblleft Virasoro modes"
\begin{align}
	L_{n , p} := \alpha ^{\mu} _{n} \alpha ^{\nu} _{p} \eta _{\mu \nu}                                                         & = 0 , \ \forall \ n , p \in \mathbb{Z} , \label{eqn:"virasoro"-modes-1} \\
	\widetilde{L}_{n , p} := \alpha ^{\mu} _{n} (\alpha ^{\nu} _{p})^{*} \eta _{\mu \nu}                                       & = 0 , \ n \neq p , \label{eqn:"virasoro"-modes-2}                       \\
	\sum _{n} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) & = 0 \label{eqn:"virasoro"-modes-sum} .
\end{align}
Constraint \eqref{eqn:"virasoro"-modes-2} implies that we only have $D$ independent expansion modes for each field $X^{\mu}$, which for consistency as we will see later means $\alpha ^{\mu} _{- p} = \alpha ^{\mu} _{p} , \ p \leq d = D - 1$ and $\alpha ^{\mu} _{n} = 0 , \ \forall \ |n| > d$, so we have a truncated solution. This is not surprising, since because space-time is discrete we expect wavelengths smaller than the granular structure to be ruled out.

@@

We now seek to quantize the Klein-Gordon string by means of covariant canonical quantization, in a manner much similar to those found in (\cite{Tong2009Lectures},\cite{Green2012Superstring}). The string coordinates $X^{\mu}$ and it's conjugate momentum $\Pi ^{\nu}$ are turned into operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$, with the Poisson brackets $\{ . , . \}$ being replaced by commutators $\{ . , . \} \rightarrow - i [ . , . ]$:
\begin{align}
	\left[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \right] & = i \delta (\sigma - \sigma ') \eta ^{\mu \nu} \label{eqn:X-P-commutator}                                              \\
	\left[ \Hat{X}^{\mu} , \Hat{X}^{\nu} \right]                                     & = 0 = \left[ \Hat{\Pi}^{\mu} , \Hat{\Pi}^{\nu} \right] \label{eqn:X-X-P-P-commutators}                                 \\
	\left[ \Hat{a}^{\mu} _{n} , \Hat{a}^{\nu} _{p} \right]                           & = 0 = \left[ (\Hat{a}^{\mu} _{n})^{\dagger} , (\Hat{a}^{\nu} _{p})^{\dagger} \right] \label{eqn:a-a-a*-a*-commutators} \\
	\left[ \Hat{a}^{\mu} _{n} , (\Hat{a}^{\nu} _{p})^{\dagger} \right]               & = \delta _{|n| , |p|} \eta ^{\mu \nu} \label{eqn:a-a*-commutator}                                                      \\
	\left[ \Hat{x}^{\mu} , \Hat{x}^{\nu} \right]                                     & = 0 = \left[ \Hat{p}^{\mu} , \Hat{p}^{\nu} \right] \label{eqn:x-x-p-p-commutators}                                     \\
	\left[ \Hat{x}^{\mu} , \Hat{p}^{\nu} \right]                                     & = i \eta ^{\mu \nu} \label{eqn:x-p-commutator}
\end{align}

@@

@@

\section{Two Expressions for Area}\label{eqn:area-formulae}

\section{Modified Nambu Goto Equations of Motion}\label{sec:modified-eom}

\section{Relating Nambu-Goto and Polyakov analysis} \label{sec:relation-with-NG-case}

At first glance, our analysis of the Polyakov string with inverse metric correction seems to not be related to what we found in the analysis of the Nambu-Goto string. However, as pointed out in \cite{Grimshaw2010Homogenization}, wave equations with a variable speed (the result of the Nambu-Goto analysis) can be turned into Klein-Gordon equations (what we found in section \ref{sec:inverse-metric-Polyakov}). While their work deals only with space-varying wave speed, it is straightforward to generalise the procedure to also include time dependence.
